\vspace{-.5cm} Lights: a generalized joint model for high-dimensional multivariate longitudinal data and censored durations \vspace{.5cm}

### 2021-03-08 paper.tex
Update the condition of increasing number of Monte Carlo samples

\paragraph*{The QNMCEM algorithm.}
Algorithm~\ref{alg:QNMCEM} describes the main steps of the resulting QNMCEM algorithm to solve the optimization problem~\eqref{eq:optim-pb}.

>>>>

\paragraph*{The QNMCEM algorithm.}
Algorithm~\ref{alg:QNMCEM} describes the main steps of the resulting QNMCEM algorithm to solve the optimization problem~\eqref{eq:optim-pb}. The $Condition$ in algorithm~\ref{alg:QNMCEM} is cv$(\Delta_{\text{rel}}^{(w+1)}) >$ cv$(\Delta_{\text{rel}}^{(w)})$, where cv$(\Delta_{\text{rel}}^{(w)})$ is coefficient of variation at the $(w + 1)$-th iteration computed as
\begin{equation*}
  \label{eq:coefficient_variation}
  \text{cv}(\Delta_{\text{rel}}^{(w+1)})= \dfrac{\text{sd}(\Delta_{\text{rel}}^{(w-1)}, \Delta_{\text{rel}}^{(w)}, \Delta_{\text{rel}}^{(w+1)})}{\text{mean}(\Delta_{\text{rel}}^{(w-1)}, \Delta_{\text{rel}}^{(w)}, \Delta_{\text{rel}}^{(w+1)})},
\end{equation*}
where sd(.) and mean(.) are the sample standard deviation and mean functions respectively and relative difference $\Delta_{\text{rel}}^{(w+1)}$ is given by 
\begin{equation*}
  \label{eq:relative_difference}
  \Delta_{\text{rel}}^{(w+1)} = \text{max} \Big\{\dfrac{|\theta^{(w+1)} - \theta^{(w)}|}{|\theta^{(w)}| + \epsilon } \Big\}
\end{equation*}
